\begin{thebibliography}{10}

\bibitem{time-expanded}
	{\sc Pyrga} Evangelia a kol.
	\emph{Efficient models for timetable information in public
	transportation}.
	J. Exp. Algorithmics. 12:2.4:1--2.4:39. 2008-06.

\bibitem{time-dependent}
	{\sc Gerth~Stølting} Brodal, {\sc Riko} Jacob.
	\emph{Time-dependent networks as models to achieve fast exact
	time-table queries}. 
	Electronic Notes in Theoretical Computer Science.
	92:3 -- 15. 2004.

\bibitem{CH}
	{\sc Geisberger}, Robert.
	\emph{Contraction of timetable networks with realistic transfers}.
	CoRR.
	abs/0908.1528. 2009.

\bibitem{RAPTOR}
	{\sc Delling}, Daniel, {\sc Pajor} Thomas, {\sc Werneck} Renato~F.
	\emph{Round-based public transit routing.}
	Transportation Science.
	49(3):591--604. 2015.

\bibitem{OSM}
	{\sc přispěvatelé OSM}.
	\emph{OpenStreetMap} [online]
	2017 [cit. 2017-07-15].\\
	Dostupné z~\url{http://www.openstreetmap.org/about}

\bibitem{bakalarka}
	{\sc Pokorný}, Tomáš.
	\emph{Hledání pěších cest v~mapě}.
	Praha, 
	2014.
	Bakalářská práce. Matematicko-fyzikální fakulta, Katerda aplikované
	matematiky.

\bibitem{SRTM}
	{\sc National Aeronautics and Space Administration.}
	\emph{The Shuttle Radar Topography Mission} [online]. 
	2009-06-17 [cit. 2014-05-04]. \\
	Dostupné z: \url{http://www2.jpl.nasa.gov/srtm/}.

\bibitem{GTFS}
	{\sc Google.}
	\emph{General Transit Feed Specification} [online]. 
	2017 [cit. 2017-07-15]. \\
	Dostupné z: \url{https://developers.google.com/transit/gtfs/reference/}.

\bibitem{PBF}
	{\sc Google.}
	\emph{Protocol Buffers} [online]. 
	2012-04-02 [cit. 2014-05-05]. \\
	Dostupné z: \url{https://developers.google.com/protocol-buffers/}.

\bibitem{JSON}
	{\sc ECMA}.
	\emph{The {JSON} data interchange format} [online].
	Technical Report Standard ECMA-404 1st Edition.
	2013-10 [cit. 2017-07-15].\\
	Dostupné z:
	\url{http://www.ecma-international.org/publications/files/ECMA-ST/ECMA-404.pdf}

\bibitem{GeoJSON}
	{\sc Butler}, H. {\sc Daly}, M. a kol.
	\emph{The GeoJSON format} [online].
	RFC 7946.
	2016-08 [cit. 2017-07-15].
	Dostupné z: \url{https://tools.ietf.org/html/rfc7946}

\bibitem{XML}
	{\sc Bray}, Tim. {\sc Paoli}, Jean a kol.
	{\em Extensible Markup Language (XML) 1.0 (Fifth Edition)} [online].
	W3C.
	2008 [cit. 2017-07-15].
	Dostupné z:
	\url{http://www.w3.org/TR/REC-xml/}

\bibitem{GPX}
	\emph{GPX: the GPS Exchange Format} [online]. 
	2017 [cit. 2017-07-15].\\ 
	Dostupné z: \url{http://www.topografix.com/gpx.asp}

\bibitem{WGS84}
	{\sc National Imagery and Mapping Agency.}
	\emph{World geodetic system 1984} [online]. 
	3. vydání, 1. dodatek.
	2000-01-03 [cit. 2017-07-15]. \\
	Dostupné z: \url{http://earth-info.nga.mil/GandG/publications/tr8350.2/wgs84fin.pdf}.

\bibitem{UTM}
	{\sc Hager} JW, {\sc Behensky} JF, {\sc Drew} BW.
	\emph{The universal grids: Universal Transverse Mercator (UTM) and Universal 
	Polar Stereographic (UPS)} [online].
	Tech. Rep. TM 8358.2, Defense Mapping Agency.
	1989, [cit. 2017-07-15].\\
	Dostupné z: \url{http://earth-info.nga.mil/GandG/publications/tm8358.2/TM8358_2.pdf}.

\bibitem{LibUCW}
	{\sc Mareš}, Martin a kol.
	\emph{LibUCW} [online].
	2016 [cit. 2017-07-15].\\
	Dostupné z: \url{https://www.ucw.cz/libucw/}	

\bibitem{Flask}
	\emph{Flask Documentation} [online].
	2017. [cit. 2017-07-15].\\
	Dostupné z: \url{http://flask.pocoo.org/docs}

\bibitem{mj-ga}
	{\sc Mareš}, Martin.
	\emph{Krajinou grafových algoritmů}. [online]
	ITI Series.
	2007 [cit. 2017-07-15].\\
	Dostupné z: \url{http://mj.ucw.cz/vyuka/ga/}

\end{thebibliography}
